Andres Karjus

### 2018-06-05 index.Rmd
fixes to redesign 2

<IMG SRC="IMG_2657.jpg" ALIGN="right" BR CLEAR="left" style="margin-left:10px; width: 50%; height: auto;"; /> 
<div style="text-align: justify"> 
I am a PhD student in linguistics based at the [Centre for Language Evolution at the University of Edinburgh](http://www.lel.ed.ac.uk/cle/), working on lexical dynamics and evolutionary variant selection in language with [Kenny Smith](http://www.lel.ed.ac.uk/~kenny), [Simon Kirby](http://www.lel.ed.ac.uk/~simon) and [Richard A. Blythe](http://www2.ph.ed.ac.uk/~rblythe3/), utilizing massive corpora and natural language processing to hunt traces of selection and competition in language. This research is supported by a Kristjan Jaak scholarship from the Archimedes Foundation of Estonia. I am also affiliated as a (part-time) junior researcher with the University of Tartu [EKKAM](http://ekkam.ut.ee/en/) sociolinguistics group, working on data visualization and agent-based models. I am also engaged in [teaching and consulting](https://andreskarjus.github.io/#teaching,_consulting_&_R workshops) data sciency things for the humanities. On the right is the picture obligatory for all academic home pages to subtly suggest that in fact I do not spend _all_ my time in the office at all.

>>>>

<IMG SRC="IMG_2657.jpg" ALIGN="right" BR CLEAR="left" style="margin-left:10px; width: 49%; height: auto;"; /> 
<div style="text-align: justify"> 
I am a PhD student in linguistics based at the [Centre for Language Evolution at the University of Edinburgh](http://www.lel.ed.ac.uk/cle/), working on lexical dynamics and evolutionary variant selection in language with [Kenny Smith](http://www.lel.ed.ac.uk/~kenny), [Simon Kirby](http://www.lel.ed.ac.uk/~simon) and [Richard A. Blythe](http://www2.ph.ed.ac.uk/~rblythe3/), utilizing massive corpora and natural language processing to hunt traces of selection and competition in language. This research is supported by a Kristjan Jaak scholarship from the Archimedes Foundation of Estonia. I am also affiliated as a (part-time) junior researcher with the University of Tartu [EKKAM](http://ekkam.ut.ee/en/) sociolinguistics group, working on data visualization and agent-based models. I am also engaged in [teaching and consulting](https://andreskarjus.github.io/#teaching-consulting-r-workshops) data sciency things for the humanities and social sciences. On the right is the picture obligatory for all academic home pages to subtly suggest that in fact I do not spend _all_ my time in the office at all.
